### 2020-04-27 cv/cv-body.tex
Update a report
No photos; small tweaks
Add preprint

@@

Fisheries.

@@

\begin{description}
\tightlist
\item[2018]
\textbf{Anderson, S.C.}, E.A. Keppel, and A.M. Edwards. A reproducible
data synopsis for over 100 species of British Columbia groundfish.
Canadian Science Advisory Secretariat (CSAS) Research Document 2019/041.
In press.
\item[2018]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. Canadian Science Advisory Secretariat (CSAS)
Research Document. Accepted at regional peer-review meeting October
2018.
\end{description}

>>>>

\hypertarget{preprints}{%
\section{Preprints}\label{preprints}}

\begin{description}
\tightlist
\item[2020]
\textbf{Anderson, S.C.}, A.M. Edwards, M. Yerlanov, N. Mulberry, J.
Stockdale, S.A. Iyaniwura, R.C. Falcao, M.C. Otterstatter, M.A.\ Irvine,
N.Z. Janjua, D. Coombs, C. Colijn. Estimating the impact of COVID-19
control measures using a Bayesian model of physical distancing. medRxiv
2020.04.17.20070086. \url{https://doi.org/10.1101/2020.04.17.20070086}.
\end{description}

@@

Fisheries. \url{https://doi.org/10.1002/fsh.10441}.

@@

\begin{description}
\tightlist
\item[2019]
\textbf{Anderson, S.C.}, Keppel, E.A., Edwards, A.M. 2019. A
reproducible data synopsis for over 100 species of British Columbia
groundfish. DFO Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version})
\item[2018]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. Canadian Science Advisory Secretariat (CSAS)
Research Document. Accepted at regional peer-review meeting October
2018. In press.
\end{description}
